Paper 1: Vitis

### 2018-02-06 Paper-1-Vitis.Rmd
Commit from RStudio

>>>>

We next tested each of the variables for *Vitis amurensis*.

```{r}
am_all <- read_excel("R_DilP_Vitis_all_added.xlsx", sheet = "amurensis.all.90")
am_all$year <- as.factor(am_all$year)
am_all$petiole.width <- as.numeric(am_all$petiole.width)
am_all$petiole.width.area <- as.numeric(am_all$petiole.width.area)
am_all$petiole.area <- as.numeric(am_all$petiole.area)
am_all$blade.area <- as.numeric(am_all$blade.area)
am_all$feret.diameter <- as.numeric(am_all$feret.diameter)
am_all$major.feret <- as.numeric(am_all$major.feret)
am_all$leaf.area <- as.numeric(am_all$leaf.area)
am_all$perimeter <- as.numeric(am_all$perimeter)
am_all$internal.perimeter <- as.numeric(am_all$internal.perimeter)
am_all$feret.diameter.ratio <- as.numeric(am_all$feret.diameter.ratio)
am_all$tooth.area.perimeter <- as.numeric(am_all$tooth.area.perimeter)
am_all$tooth.area.int.perimeter <- as.numeric(am_all$tooth.area.int.perimeter)
am_all$tooth.area.blade.area <- as.numeric(am_all$tooth.area.blade.area)
am_all$teeth.perimeter <- as.numeric(am_all$teeth.perimeter)
am_all$teeth.int.perimeter <- as.numeric(am_all$teeth.int.perimeter)
am_all$perimeter.area <- as.numeric(am_all$perimeter.area)
am_all$perimeter.ratio <- as.numeric(am_all$perimeter.ratio)
am_all$compactness <- as.numeric(am_all$compactness)
am_all$shape.factor <- as.numeric(am_all$shape.factor)
am_all$teeth.blade.area <- as.numeric(am_all$teeth.blade.area)
str(am_all)
t.test(am_all$total.teeth~am_all$year, var.equal = TRUE)
t.test(am_all$feret.diameter.ratio~am_all$year, var.equal = TRUE)
t.test(am_all$tooth.area.perimeter~am_all$year, var.equal = TRUE)
t.test(am_all$tooth.area.int.perimeter~am_all$year, var.equal = TRUE)
t.test(am_all$average.tooth.area~am_all$year, var.equal = TRUE)
t.test(am_all$tooth.area.blade.area~am_all$year, var.equal = TRUE)
t.test(am_all$teeth.perimeter~am_all$year, var.equal = TRUE)
t.test(am_all$teeth.int.perimeter~am_all$year, var.equal = TRUE)
t.test(am_all$perimeter.area~am_all$year, var.equal = TRUE)
t.test(am_all$perimeter.ratio~am_all$year, var.equal = TRUE)
t.test(am_all$compactness~am_all$year, var.equal = TRUE)
t.test(am_all$shape.factor~am_all$year, var.equal = TRUE)
t.test(am_all$teeth.blade.area~am_all$year, var.equal = TRUE)
```
